---
title: "Mini Data-Analysis Deliverable 2"
output: github_document
self_contained: true
editor_options: 
  markdown: 
    wrap: sentence
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by: 

- Making summary tables and graphs 
- Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.* 

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission. 

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
```

# Task 1: Process and summarize your data 

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions. 

### 1.1 (1 point) 

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->
1.  Which ward(s) have the most fire-safe apartment buildings? Is this correlated with year built?
2.  Which ward(s) have the most barrier-free, accessible apartment buildings? Is this correlated with year built?
3.  What are the most common window types? Is this correlated with ward or year built?
4.  Does the year that the apartment building was built influence whether or not it has air conditioning?
<!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4. Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7. Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks: 

8. Create a graph that has at least two geom layers. 
9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
#### Which ward(s) have the most fire-safe apartment buildings? Is this correlated with year built?

**Summarizing:**  I will compute the number of observations for a new categorical variable that indicates whether an apartment building is or is not fire-safe; here, fire-safe is defined as a building with fire alarms, exterior fire escapes, and sprinkler systems. By doing this, I'll be able to see the ward(s) that have the most fire-safe apartment buildings. Moreover, I'll be able to see the breakdown of fire-safe, partially fire-safe, or not fire-safe buildings in each ward.

```{r}
# creates a new categorical variable that says if an apartment building is or is not fire-safe
apt_buildings <- apt_buildings %>%
  filter(!ward == "YY") %>%
  mutate(fire_safe = 
           # filters according to criteria
           case_when(fire_alarm == "YES" & sprinkler_system == "YES" & exterior_fire_escape == "YES" ~ "YES",
                     fire_alarm == "YES" & sprinkler_system == "YES" ~ "PARTIAL",
                     fire_alarm == "YES" & exterior_fire_escape == "YES" ~ "PARTIAL",
                     TRUE ~ "NO")) 

# counts the number of observations for the fire-safe variable per ward
fire_safe <- apt_buildings %>%
  count(ward, fire_safe) # counts the number of buildings that are or are not fire-safe 
print(fire_safe)
```

**Graphing:** I will create a bar graph as this will allow me to see the breakdown of fire-safe, partially fire-safe, or not fire-safe buildings in each ward. I will also have labels that will display the "n" value at the top of each bar for increased clarity.

```{r}
bar_fire <- fire_safe %>%
  ggplot(aes(x = ward, # plots with wards as the x-axis
             y = n, # plots with the count as the y-axis
             fill = fire_safe)) + # groups by fire-safe categorization
  geom_bar(stat = "identity", 
           position = position_dodge(), # staggers bars side by side
           width = 0.8, # adjusts bar width
           alpha = 0.5) + # creates a bar plot at half transparency
  geom_text(aes(label = n), # labels each bar with the n
            position = position_dodge(0.9), # adjusts placement of labels
            size = 2, # adjusts size of labels
            vjust = -0.5) # adjusts vertical placement of labels

print(bar_fire)
```

#### Which ward(s) have the most barrier-free, accessible apartment buildings? Is this correlated with year built?

**Summarizing:** I will compute the number of observations for a new categorical variable that indicates whether an apartment building is or is not barrier-free and accessible; this is defined as a building with barrier-free accessibility entrances, accessible parking spaces, an elevator(s), as well as at least one barrier-free accessible unit. By doing this, I'll be able to see the ward(s) that have the most barrier-free, accessible apartment buildings.

```{r}
# creates a new categorical variable that says if an apartment building is or is not accessible
apt_buildings <- apt_buildings %>%
  filter(!ward == "YY") %>% 
  mutate(accessible = 
           # filters according to criteria
           case_when(barrier_free_accessibilty_entr == "YES" & 
                       no_of_accessible_parking_spaces >0 & 
                       no_of_elevators >0 &
                       no_barrier_free_accessible_units >0 ~ "YES",
                     TRUE ~ "NO")) 

# counts the number of observations for the accessible variable per ward
accessible <- apt_buildings %>%
  count(ward, accessible) # counts the number of buildings that are or are not accessible 
print(accessible)
```

**Graphing:** I will create a bar graph as this will allow me to see the breakdown of barrier free, accessible buildings in each ward. I will also have labels that will display the "n" value at the top of each bar for increased clarity.

```{r}
bar_accessible <- accessible %>%
  ggplot(aes(x = ward, # plots with wards as the x-axis
             y = n, # plots with the count as the y-axis
             fill = accessible)) + # groups by accessible categorization
  geom_bar(stat = "identity", 
           position = position_dodge(), # staggers bars side by side
           width = 0.8, # adjusts bar width
           alpha = 0.5) + # creates a bar plot at half transparency
  geom_text(aes(label = n), # labels each bar with the n
            position = position_dodge(0.9), # adjusts placement of labels
            size = 2, # adjusts size of labels
            vjust = -0.5) # adjusts vertical placement of labels

print(bar_accessible)
```

#### What are the most common window types? Is this correlated with ward or year built?

**Summarizing:** I will compute the range, mean, and median of years built across the groups of window type. I will also count the number of buildings within each. Altogether, this will allow me to examine if there is a trend between when a certain window type is included and the year the apartment building was built, as well as its popularity.

```{r}
window_summary <- apt_buildings %>%
  group_by(window_type) %>% # groups by window type
  summarise(year_earliest = min(year_built, na.rm = TRUE), # identifies earliest year 
            year_latest = max(year_built, na.rm = TRUE), # identifies latest year
            year_mean = mean(year_built, na.rm = TRUE), # identifies average year 
            year_med = median(year_built, na.rm = TRUE), # identifies median year 
            year_n = n()) # identifies number of buildings 

print(window_summary)
```

**Graphing:** I will create a density graph of the window types as this will allow me to visualize the distribution of data over the years built. As there will be overlap, I will customize the alpha transparency to ensure that all three graphs will be visible.

```{r}
density_window <- apt_buildings %>%
  filter(!is.na(window_type) & !is.na(year_built)) %>% # removes any missing data
  ggplot(aes(x = year_built, # plots with years as the x-axis
             fill = window_type, colour = window_type)) + # groups based on window type
  geom_density(alpha = 0.25) # customizes alpha transparency of density plot

print(density_window)
```

#### Does the year that the apartment building was built influence whether or not it has air conditioning?

**Summarizing:** I will compute the range, mean, and median of years built across the types of air conditioning. I will also count the number of buildings within each. Altogether, this will allow me to examine if there is a trend between whether a building has air conditioning and the year the apartment building was built, as well as which air conditioning method is most employed.

```{r}
ac_summary <- apt_buildings %>%
  group_by(air_conditioning) %>% # groups by window type
  summarise(year_earliest = min(year_built, na.rm = TRUE), # identifies earliest year 
            year_latest = max(year_built, na.rm = TRUE), # identifies latest year
            year_mean = mean(year_built, na.rm = TRUE), # identifies average year 
            year_med = median(year_built, na.rm = TRUE), # identifies median year 
            year_n = n()) # identifies number of buildings 

print(ac_summary)
```

**Graphing:** I will create a density graph of the air conditioning methods as this will allow me to visualize the distribution of data over the years built. As there will be overlap, I will customize the alpha transparency to ensure that all three graphs will be visible.

```{r}
density_ac <- apt_buildings %>%
  filter(!is.na(air_conditioning) & !is.na(year_built)) %>% # removes any missing data
  ggplot(aes(x = year_built, # plots with years as the x-axis
             fill = air_conditioning, colour = air_conditioning)) + # groups based on air conditioning
  geom_density(alpha = 0.25) # customizes alpha transparency of density plot

print(density_ac)
```

<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->
Based on the activities I've done, I feel that I am somewhat closer to answering my research questions. I have gained a better insight into the dataset, as well as the relationship between my variables of interest; for example, while double pane windows have been commonly employed since the early 1800s, it appears that the use of single pane windows has ceased. Though much of the knowledge is preliminary, I am now able to further refine my research questions and identify which questions are worthy of further investigation. Moving forward, I would like to delve into my definitions of "fire-safe" and "accessible" buildings by looking at the year they were built. My current hypothesis is that those who were built later are more fire-safe and accessible. This is because unlike with window type and air conditioning, these are traits that are less likely to be implemented after the building is built.
<!----------------------------------------------------------------------------->

# Task 2: Tidy your data 

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->
Based on the definition above, I feel that my data is semi-tidy. The eight variables I chose from the dataset are "air_conditioning", "amenities", "balconies", "barrier_free_accessibility_entr", "bike_parking", "exterior_fire_escape", "fire_alarm", and "garbage_chutes". Of these, six of the eight are tidy; the two untidy ones are "amenities" and "bike_parking" as each cell has multiple values. It would therefore be of use to separate the data within each of them into additional, more specific columns. 
<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->
**Reasoning:** I will be tidying the data and then untidying it to its original state. As I mentioned above, "amenities" and "bike_parking" are untidy variables. This is because both consists of multiple observations; for example, bike_parking lists both inside and outside bike parking. Therefore, to tidy this I will be splitting amenities to five separate columns - one for child play area, one for exercise rooms, one for sauna, one for pools, and one for recreation. I will also be splitting bike_parking to two separate columns - one for indoor bike parking, and one for outdoor bike parking.

#### Subsetting Data
```{r}
# creates a separate dataset with the eight variables of interest from apt_buildings
apt_buildings_sub <- apt_buildings %>%
  select(air_conditioning:garbage_chutes)
print(apt_buildings_sub)
```

#### Tidying Data

```{r}
# subsetting
apt_buildings_tidy <- apt_buildings_sub %>%
  # amenities 
  mutate(amenities_child = # creates a column specific for "child play area"
           case_when(amenities = str_detect(amenities, "Child play area") ~ "YES",
                     TRUE ~ "NO"),
         amenities_exercise = # creates a column specific for "indoor exercise room"
           case_when(amenities = str_detect(amenities, "Indoor exercise room") ~ "INDOOR",
                     TRUE ~ "NO"),
         amenities_sauna = # creates a column specific for "sauna"
           case_when(amenities = str_detect(amenities, "Sauna") ~ "YES",
                     TRUE ~ "NO"),
         amenities_pool = # creates a column specific for "indoor pool" and "outdoor pool"
           case_when(amenities = str_detect(amenities, "Indoor pool") ~ "INDOOR",
                     amenities = str_detect(amenities, "Outdoor pool") ~ "OUTDOOR",
                     TRUE ~ "NO"),
         amenities_rec = # creates a column specific for "indoor recreation room", "outdoor rec facilities"
           case_when(amenities = str_detect(amenities, "Indoor recreation room") ~ "INDOOR",
                     amenities = str_detect(amenities, "Outdoor rec facilities") ~ "OUTDOOR",
                     TRUE ~ "NO"),
         ) %>%
  # bike parking
  mutate(# creates a column specific for the number of indoor bike parking spots
         bike_parking_in = str_c(str_match(bike_parking, "(.*) indoor parking spots")[, 2]),
         # creates a column specific for the number of outdoor bike parking spots
         bike_parking_out = str_c(str_match(bike_parking, "(.*) outdoor parking spots$")[, 2]),
         bike_parking_out = str_sub(bike_parking_out, -2)
         ) %>%
  # removing untidy columns
  select(-c(amenities, bike_parking))
```

```{r}
# previews tidied dataset
print(apt_buildings_tidy)
```

#### Untidying Data

```{r}
apt_buildings_untidy <- apt_buildings_tidy %>%
  # amenities 
  mutate(amenities_child = # reverts text back to "Child play area"
           case_when(amenities_child = str_detect(amenities_child, "YES") ~ "Child play area",
                     TRUE ~ NA_character_),
         amenities_exercise = # reverts text back to "Indoor exercise room"
           case_when(amenities_exercise = str_detect(amenities_exercise, "INDOOR") ~ "Indoor exercise room",
                     TRUE ~ NA_character_),
         amenities_sauna = # reverts text back to "Sauna"
           case_when(amenities_sauna = str_detect(amenities_sauna, "YES") ~ "Sauna",
                     TRUE ~ NA_character_),
         amenities_pool = # reverts text back to "Indoor pool" and "Outdoor pool"
           case_when(amenities_pool = str_detect(amenities_pool, "INDOOR") ~ "Indoor pool",
                     amenities_pool = str_detect(amenities_pool, "OUTDOOR") ~ "Outdoor pool",
                     TRUE ~ NA_character_),
         amenities_rec = # reverts text back to "Indoor recreation room" and "Outdoor rec facilities"
           case_when(amenities_rec = str_detect(amenities_rec, "INDOOR") ~ "Indoor recreation room",
                     amenities_rec = str_detect(amenities_rec, "OUTDOOR") ~ "Outdoor rec facilities",
                     TRUE ~ NA_character_),) %>%
  # bike parking
  mutate(bike_parking_in = # includes "indoor parking spots" after number
           case_when(bike_parking_in >=0 ~ paste0(bike_parking_in, " indoor parking spots"),
                     TRUE ~ NA_character_),
         bike_parking_out = # includes "outdoor parking spots" after number
           case_when(bike_parking_out >=0 ~ paste0(bike_parking_out, " outdoor parking spots"),
                     TRUE ~ NA_character_),
         ) %>%
  # collapses observations into a single column for amenities
  unite("amenities", amenities_child:amenities_rec, na.rm = TRUE, remove = TRUE, sep = ", ") %>%
  # collapses observations into a single column for bike_parking
  unite("bike_parking", bike_parking_in:bike_parking_out, na.rm = TRUE, remove = TRUE, sep = " and ")
```

```{r}
# previews untidied dataset
print(apt_buildings_untidy)
```

<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  Which ward(s) have the most fire-safe apartment buildings?
2.  Which ward(s) have the most barrier-free, accessible apartment buildings?

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->
As mentioned above, I would like to delve into my definitions of "fire-safe" and "accessible" buildings by looking at the year they were built moving forward. My current hypothesis is that those who were built later are more fire-safe and accessible. This is because unlike with my other questions relating window type and air conditioning to year built, these are traits that are more inherent to the building's construction. Moreover, the two questions I chose yielded more interesting results in Exercise 1. 
<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidying, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.) 

<!--------------------------- Start your work below --------------------------->

```{r}
apt_buildings_fire <- apt_buildings %>%
  # selecting variables of interest
  select(id, year_built, ward, fire_alarm, sprinkler_system, exterior_fire_escape) %>%
  # removes ward YY as it's not a real ward
  filter(!ward == "YY") %>% 
  # creates fire_safe variable according to definition
  mutate(fire_safe = 
           # filters according to criteria
           case_when(fire_alarm == "YES" & sprinkler_system == "YES" & exterior_fire_escape == "YES" ~ "YES",
                     fire_alarm == "YES" & sprinkler_system == "YES" ~ "PARTIAL",
                     fire_alarm == "YES" & exterior_fire_escape == "YES" ~ "PARTIAL",
                     TRUE ~ "NO")) %>%
  # removes observations that are missing data required for fire-safe definition
  subset(!is.na(fire_alarm) & !is.na(sprinkler_system) & !is.na(exterior_fire_escape))

print(apt_buildings_fire)
```

```{r}
apt_buildings_accessible <- apt_buildings %>%
  # selecting variables of interest
  select(id, year_built, ward, barrier_free_accessibilty_entr, no_of_accessible_parking_spaces, 
         no_of_elevators, no_barrier_free_accessible_units) %>%
  # removes ward YY as it's not a real ward
  filter(!ward == "YY") %>% 
  # creates accessible variable according to definition
  mutate(accessible = 
           # filters according to criteria
           case_when(barrier_free_accessibilty_entr == "YES" & 
                       no_of_accessible_parking_spaces >0 & 
                       no_of_elevators >0 &
                       no_barrier_free_accessible_units >0 ~ "YES",
                     TRUE ~ "NO")) %>%
  # removes observations that are missing data required for accessible definition
  subset(!is.na(barrier_free_accessibilty_entr) & !is.na(no_of_accessible_parking_spaces) 
         & !is.na(no_of_elevators) & !is.na(no_barrier_free_accessible_units))

print(apt_buildings_accessible)
```

<!----------------------------------------------------------------------------->

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: Which ward(s) have the most barrier-free, accessible apartment buildings? Is this correlated with year built?

**Variable of interest**: no_barrier_free_accessible_units

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->
```{r}
# fits a linear model between the number of barrier free accessible units (Y) and year built (X)
model <- lm(no_barrier_free_accessible_units ~ year_built, apt_buildings_accessible)

print(model)
```
<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

I chose to look at the p-value for the intercept and slope of the linear model I created. The results can be seen in the fifth column (titled "p-value") in the first and second row respectively. 

```{r}
library(broom) # loads the broom library
tidy(model) # this function constructs a tibble that summarizes the model’s statistical findings
```
<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->
```{r}
# loads relevant library
library(here)

# exporting csv
write.csv(accessible, here("output", "apt_buildings_accessible_summ.csv")) # "here" dictates file location
```
<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->
```{r}
# exports R binary file
saveRDS(model, here("output", "model.RDS")) # "here" dictates file location
```


```{r}
# loading R binary file
readRDS(here("output", "model.RDS"), refhook = NULL) # "here" locates file of interest
```
<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist 

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. 

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone. 

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2. 

### Attribution

Thanks to Victor Yuan for mostly putting this together.
